Conjure: Summoning Proxies from Unused Address Space

### 2019-08-30 paper/figures.tex
quick fix and figure 6 arch redone.

\newcommand{\TabApplications}{
\begin{table}[t]
    \centering
    \begin{tabular}{l|ccccc}
            & \rot{OSSH~\cite{ossh}} &
              \rot{\texttt{obfs4}~\cite{obfs4}} &
              \rot{Mask Sites} &
              \rot{TLS eSNI} & \rot{WebRTC} \\
            \hline
            Active probe resistant  & \no  & \yes & \yes & \yes & \yes \\
            Randomized or Tunneling & R    & R    & T    &  T   & T \\
            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
    \end{tabular}
    \medskip
    \caption{\textbf{\scheme Applications}\,---\,\rm%
    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
        ones attempt to have no discernable protocol fingerprint or headers.
        For existing protocols, we list any known attacks suggested in the literature that let censors
        passively detect them. We also list if we have implemented the application in our prototype.}
    \label{tab:applications}
\end{table}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered phantom host addresses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as an innocuous host, such as by
        forwarding pakcets to a mask site.}
    \label{fig:implementation}
\end{figure}
}

>>>>

\newcommand{\TabApplications}{
\begin{table}[t]
    \centering
    \begin{tabular}{l|ccccc}
            & \rot{OSSH~\cite{ossh}} &
              \rot{\texttt{obfs4}~\cite{obfs4}} &
              \rot{Mask Sites} &
              \rot{TLS eSNI} & \rot{WebRTC} \\
            \hline
            Active probe resistant  & \yes  & \yes & \yes & \yes & \yes \\
            Randomized or Tunneling & R    & R    & T    &  T   & T \\
            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
    \end{tabular}
    \medskip
    \caption{\textbf{\scheme Applications}\,---\,\rm%
    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
        ones attempt to have no discernable protocol fingerprint or headers.
        For existing protocols, we list any known attacks suggested in the literature that let censors
        passively detect them. We also list if we have implemented the application in our prototype.}
    \label{tab:applications}
\end{table}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-flow1.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies registrations, notifying all
        cores when a new registration is received (green dashed registration flow). The detector also
        identifies packets associated with registered flows (by connection 4-tuple) and diverts them
        to a local application which handles proxying connections(purple dotted flow). The local 
        application determines which proxy the flow should use based on a parameter specified by 
        the client in the registration and initializes a goroutine to handle forwarding. 
        \\\hspace{\textwidth}
        A censor trying to interfere in this
        connection would need to co-opt the clients IP address in a precise window (after the 
        registration but before the client connects to the phantom) and correctly guess the phantom hosts 
        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
        At this point their connection will fail in a manor specific to the proxy that the client specified
        in the registration (e.g. connecting to OSSH without knowledge of the preshared secret).}
    \label{fig:implementation}
\end{figure}
}

### 2019-08-30 paper/related.tex
quick fix and figure 6 arch redone.

Traditionally, proxies deployed for censorship are eventually identified and
blocked by the censor. Several proposals have been made to carefully control
the distribution of proxy addresses, using social connections and
reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
information secret is challenging; additionally, censors often employ active
scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
networking generally assumes that clients have no secret information, and
instead relies on the  collateral damage that would result from blocking all
the potential decoy destinations. \scheme furthers this goal by creating a
large number of destinations out of the dark space. A similar approach was
conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
connect to pools of addresses that are volunteered to run Tor bridge nodes.
DEFIANCE also requires volunteer web servers to run specialized servers to
distribute information. Unlike \scheme, DEFIANCE was not designed to run at an
ISP, and invovles many moving parts that present single points of failure if
blocked by a censor. In contrast, \scheme has a relatively simple yet flexible
design, allowing it to easily respond to censors.
Another similar approach was
taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
set of dummy destinations. CensorSpoofer, however, could only send information
in one direction---to the client---and had to rely on a separate out-of-band
channel for client-to-proxy communication. As an alternative approach,
FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
run Flash- or WebRTC-based proxies within their browser to allow censored users
to connect to the Tor network with the potential to greatly increase the
number. In practice, these proxies served a very small number of users, as
compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

Traditionally, proxies deployed for censorship are eventually identified and
blocked by the censor. Several proposals have been made to carefully control
the distribution of proxy addresses, using social connections and
reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
information secret is challenging; additionally, censors often employ active
scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
networking generally assumes that clients have no secret information, and
instead relies on the  collateral damage that would result from blocking all
the potential decoy destinations. \scheme furthers this goal by creating a
large number of destinations out of the dark space. A similar approach was
conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
connect to pools of addresses that are volunteered to run Tor bridge nodes.
DEFIANCE also requires volunteer web servers to run specialized servers to
distribute information. Unlike \scheme, DEFIANCE was not designed to run at an
ISP, and involves many moving parts that present single points of failure if
blocked by a censor. In contrast, \scheme has a relatively simple yet flexible
design, allowing it to easily respond to censors.
Another similar approach was
taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
set of dummy destinations. CensorSpoofer, however, could only send information
in one direction---to the client---and had to rely on a separate out-of-band
channel for client-to-proxy communication. As an alternative approach,
FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
run Flash- or WebRTC-based proxies within their browser to allow censored users
to connect to the Tor network with the potential to greatly increase the
number. In practice, these proxies served a very small number of users, as
compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
